Forecasting the 2024 U.S. Presidential Election: An Analysis for Battleground States\thanks{Code and data are available at: \url{https://github.com/krishnak30/US_elections}.}

### 2024-11-01 paper/paper.tex
commit intermediary files

\begin{document}
\maketitle
\begin{abstract}
This study employs a polls-of-polls approach to predict support for
Kamala Harris and Donald Trump in the 2024 U.S. Presidential Election,
with a focus on key battleground states to forecast the likely winner of
the electoral college. By aggregating multiple polls and applying a
weighted linear regression model with predictors like pollster
reliability, sample size, state, and recency, we estimate a higher
national support for Trump relative to Harris. Our analysis also reveals
a close competition in battleground states, with Trump holding a narrow
lead in Arizona, Georgia, and North Carolina, while Harris leads in
Michigan, Nevada, Pennsylvania, and Wisconsin. These findings underscore
the value of aggregating polls over relying on individual surveys,
offering a more comprehensive and robust forecast of electoral outcomes.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

>>>>

\begin{document}
\maketitle
\begin{abstract}
This study employs a polls-of-polls approach to predict support for
Kamala Harris and Donald Trump in the 2024 U.S. Presidential Election,
with a focus on key battleground states to forecast the likely winner of
the electoral college. By aggregating multiple polls and applying a
weighted linear regression model with predictors like pollster
reliability, sample size, state, and recency, we estimate a higher
national support for Trump relative to Harris. Our analysis also reveals
a close competition in battleground states, with Trump holding a narrow
lead in Arizona, Georgia, and North Carolina, while Harris leads in
Michigan, Nevada, Pennsylvania, and Wisconsin. These findings underscore
the value of aggregating polls over relying on individual surveys,
offering a more comprehensive and robust forecast of electoral outcomes.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, enhanced, boxrule=0pt]}{\end{tcolorbox}}\fi
